---
title: "case_study"
author: "Pei Yang Hsieh"
date: 2018-10-9
output: html_document
---

## Load data

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
data(nyc_airbnb)
```

## Rename/clean

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(starts = review_scores_location / 2) %>% 
  rename(boro = neighbourhood_group)
```

## Data exploration


```{r}
nyc_airbnb %>% 
  count(boro)

nyc_airbnb %>% 
  count(boro, neighbourhood)
```
## Some questions

* Does rating vary by neighborhood, room type, or both?
* How is price related to other variables?
* Where are rentals located?

* What's most expensive area? What about the least?
* Which listings have the most unbooked days? 
* Which area has highest densit yof listings?
* What are some host characteristics? How many listings? What's associated with ratings?

```{r}
#Does rating vary?

nyc_airbnb %>%
 group_by(neighbourhood) %>%
 summarize(median(starts, na.rm = TRUE)) %>% View

nyc_airbnb %>%
 group_by(room_type) %>%
 summarize(median(starts, na.rm = TRUE)) %>% View

airbnb_rating = nyc_airbnb %>%
 group_by(boro, room_type) %>%
 summarise(
   mean(starts, na.rm = TRUE)) 
   #spread(key = room_type, value = mean_starts))

ggplot(nyc_airbnb, aes(x = starts), color = boro) +
 geom_histogram() +
 facet_grid(~room_type)

#Where are rentals located?

nyc_airbnb %>% 
  ggplot(aes(x = longitude, y = latitude, color = boro)) +
  geom_point() +
  facet_grid(~room_type)

#What's most expensive?
nyc_airbnb %>%
 select(boro, neighbourhood, price) %>%
 filter(boro == "Brooklyn") %>%
 group_by(neighbourhood) %>%
 summarize(mean_price = mean(price, na.rm = TRUE),
           median_price = median(price, na.rm = TRUE)) %>%
 top_n(5) %>% View

nyc_airbnb %>%
 select(boro, neighbourhood, price) %>%
 filter(boro == "Brooklyn") %>%
 group_by(neighbourhood) %>%
 summarize(mean_price = mean(price, na.rm = TRUE),
           median_price = median(price, na.rm = TRUE)) %>%
 arrange(mean_price) %>% View
```

